% !TEX root = ../my-thesis.tex
%
\pdfbookmark[0]{Abstract}{Abstract}
\addchap*{Abstract}
\label{sec:abstract}

The Wendelstein 7-X (W7-X) plasma experiment is the most advanced stellarator of the HELIAS type. W7-X aims to demonstrate the feasibility of steady-state operation of a plasma experiment and the potential viability of a fusion reactor. W7-X is a device with a five-fold symmetry and with a unique magnetic field geometry created using non-planar and planar superconducting coils. It also uses the island divertor concept for managing heat and particle exhaust at the plasma-wall interfaces, which are created by divertor target plates intersecting the edge magnetic islands. The graphite divertor targets used in W7-X are designed to withstand a heat load of up to 10 $MW/m^2$, but exceeding this limit can damage the divertor structures and prevent sustained operation of the device. In order to prevent thermal overload, the positions of the edge magnetic islands with respect to the target plates can be adjusted using trim and control coils. This thesis presents an approach for inferring the edge rotational transform, a key parameter that determines the position of the magnetic islands and heat load pattern, from infrared camera data. Using an inceptnet convolutional neural network, the 520x130 input resolution is a good compromise between computational cost and network performance. When evaluating $\iota$, the rotational transform, this network is able to achieve an $rmse$ of $4.13 \cdot 10^{-3}$ and a training time of less than a day on a single GPU, which is an order of magnitude better than prior work with similar data.